---
title: "luke_presentation examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{luke_presentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

Some examples of to use the `luke_presentation` function to kick-start a new presentation with Luke's theme.

```{r}
library(lukeR)
```

# Powerpoint

**UPDATE: Powerpoint-templates are no longer included in `lukeR`, as they come with all Valtti units. The stuff below is obsolete.**

Luke has a set of Powerpoint templates. The function will simply copy one of them to a designated location. The default is current working directory, as usual.

```{r, include=FALSE, eval=FALSE}
luke_presentation(path = "example_path", type = "pp", lang="fi", ask = FALSE)

```


```{r, eval=FALSE}
luke_presentation(path = "example_path/", type = "pp", lang = "fi")
dir("example_path")
```

If the path does not exist, a prompt will ask if it should be created. 

# LaTeX Beamer

```{r}
luke_presentation(path = "example_path/", type = "beamer", lang = "se")
dir("example_path")
```

You can rename the main Beamer file `luke-beamer-template.tex` to your liking. 


